Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-10-30 Journal1/LastVersion/pr.tex
add journLal1

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-25pt}
\setlength{\dbltextfloatsep}{-20pt}
\begin{document}

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
 }

@@

So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
%\begin{equation}
%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
%\end{equation}
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).  
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

@@

@@

Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. There is no restriction on fronthaul link capacity and the number of VNFs.

>>>>

 %\pdfoutput=1
%\documentclass[conference]{IEEEtran}
\documentclass[journal,draftcls,onecolumn,12pt,twoside]{IEEEtranTCOM}
\normalsize
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\usepackage{algcompatible}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength{\columnsep}{11mm}
\captionsetup{font=footnotesize}
\captionsetup[figure]{font=small}
\newcommand{\abstractnamefont}{\normalfont\small\bfseries}
\newcommand{\abstracttextfont}{\normalfont\small}
\setlength{\belowcaptionskip}{-25pt}
\setlength{\dbltextfloatsep}{-20pt}

\begin{document}

\title{Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%\pagestyle{plain}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%%}

\author{Mojdeh Karbalaee Motalleb \and Vahid Shah-mansouri \and Saeede Parsaeefard \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
\IEEEauthorblockA{School of ECE, University of Tehran, Iran, University of Toronto, Canada}
 }

@@

So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
%\begin{equation}
%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
%\end{equation}
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).  
\vspace*{-1.5em}
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

\vspace*{-4em}

@@

\vspace*{-1em}

@@

Assume each UE in each mMTC service instance requires 0.1 bits/sec/Hz data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link and the number of VNFs have no restrictions.
